\chapter*{Introduction}

In many fields and sectors we face many problems which are solved and interpreted based upon numerical values using statistical analysis .In our case the problem is trying to augment the leads conversion rate, but how?. Take the example of a company named WISD education sells online courses. On any given day, many professionals who are interested in the courses land on their website and browse for courses. The company markets its courses on several websites and search engines like Google. Once these people land on the website, they might browse the courses or fill up a form for the course or watch some videos. When these people fill up a form providing their email address or phone number, they are classified to be a lead. Moreover, the company also gets leads through past referrals. Once these leads are acquired, employees from the sales team start making calls, writing emails, etc. Through this process, some of the leads get converted while most do not. The typical lead conversion rate at WISD education is around 30\%. To make this process more efficient, the company wishes to identify the most potential leads, also known as ‘Hot Leads’ \\If they successfully identify this set of leads, the lead conversion rate should go up as the sales team will now be focusing more on communicating with the potential leads rather than making calls to everyone.\\ In another form we will create a logistic regression model who is able to predict the probability of a conversion to specific individual professional based on different parameters .
\\Thus, to do this task we need a dataset at the first place then, a complete description for our model and its parameters , also some inferences and diagnostics to see if we could make our model more and more efficient .



